### 2015-04-06 paper_10_intro.tex
final updates before format check

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[Defect] - ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed testcases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    An example of scoring software development is presented by 
    Jones \cite{Jones2012}. The methodology looks
    for the presence of various techniques used in software engineering.  
    The methodology provides a score based upon the 
    productivity and quality increase of the technique being evaluated.  
    Points are positive or negative based upon the 
    presence of various techniques. A couple of example techniques are: 
    automated source code analysis and continuous integration.  The end 
    result is a score in range $[-10,10]$. 
    While the result is a single number score, it does not account for the 
    entirety of the software development life cycle.

@@

    Another promising research area is \textit{process mining}
    \cite{vanderAalst2012}.
    As stated by Wil van der Aalst \cite{vanderAalst2011}, 
    ``The idea of process mining is to discover, monitor
    and improve real
    processes (i.e., not assumed processes) by extracting knowledge from event logs
    readily available in today's systems.''  Creating software involves
    a vast amount of processes.  Numerous logs of raw data are collected.  
    One application of process mining in the area of software development
    was an algorithm and information for measuring a software engineering process from
    the Software Configuration Management (SCM) \cite{Rubin2007}.
    The technique creates process models 
    to understand the process of developing software and code. 
    It is less focused on the output and results,
    but it is more focused on adherence to a specified process.

@@

    Software quality is one of the most well studied aspects
    of software development.  Most of the work focuses on
    either the problems with the software or the source code.
    Quality and the number of problems with the software
    are inversely related, more problems means lower quality. 
    Quality is easy to measure, but 
    that measurement is usually very software specific.  It is easy
    to find that some software has $X$ number of problems, but
    it is nearly impossible to determine whether the quality
    of that software is better or worse than some other software
    with $X$ defects.  One piece of software can be 
    larger\footnote{Saying a piece of software is larger can be a 
    rather arbitrary statement.  It can mean the software requires 
    more computing time, has more lines of code, more documentation, 
    more hours spent on development, or some other arbitrary measure.}
    or more complex.  Thus, finding a value for quality is easier 
    than interpreting that value.  No matter the interpretation,
    the goal is to release the number of problems with the software.
    Top 10 lists have been created for techniques to remove problems
    from software \cite{Boehm2001}.  
    A number of different techniques or best practices
    for preventing defects have 
    been proposed \cite{Faizan2012}.  These are all strategies to identify
    or remove the problems before the software is completed and released
    to users.

@@

    One area of research that is focusing on the evaluation 
    of SDOs
    is \textit{software analytics}. 
    Software analytics is less focused on evaluation
    and more so on all sorts of analysis of software data.
    The earliest variants
    of software analytics were disguised as
    applications of data mining techniques to software 
    engineering data in the 
    late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
    Later the field began to emerge more heavily, but still
    remained primarily methods of data mining applied to 
    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
    Finally, The term software intelligence was proposed for the field of study
    \cite{Hassan2010}, but eventually
    the term software analytics became the dominant term for referring to the 
    field of study \cite{Buse2010, Zhang2011}.

@@

    All of these techniques are of no use if the correct data
    is not available.  Therefore, it is important to 
    identify the information that is needed to properly 
    perform software development analytics.
    Unfortunately, there are vast amounts of information that 
    need to be collected to meet the analytic needs of 
    developers and managers \cite{Buse2012}.  When the
    data and tools exists, the analytics should help an
    organization with the following tasks.
    \begin{itemize}
        \item Evaluate a project
        \item Determine what is and is not working
        \item Manage Risk
        \item Anticipate changes
        \item Evaluate prior decisions
    \end{itemize}

>>>>

        \item[Application] - A software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[Defect] - ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed testcases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    An example of scoring software development is presented by 
    Jones \cite{Jones2012}. The methodology looks
    for the presence of various techniques used in software engineering.  
    The methodology provides a score based upon the 
    productivity and quality increase of the technique being evaluated.  
    Points are positive or negative based upon the 
    presence of various techniques. Two examples of such techniques are: 
    automated source code analysis and continuous integration.  The end 
    result is a score in range $[-10,10]$. 
    While the result is a single number score, it does not account for the 
    entirety of the software development life cycle.

@@

    Another promising research area is \textit{process mining}
    \cite{vanderAalst2012}.
    As stated by Wil van der Aalst \cite{vanderAalst2011}, 
    ``The idea of process mining is to discover, monitor
    and improve real
    processes (i.e., not assumed processes) by extracting knowledge from event logs
    readily available in today's systems.''  Creating software involves
    many processes.  Numerous logs of raw data are collected.  
    One application of process mining in the area of software development
    was an algorithm and information for measuring a software engineering process from
    the Software Configuration Management (SCM) \cite{Rubin2007}.
    The technique creates process models 
    to understand the process of developing software and code. 
    It is less focused on the output and results,
    but it is more focused on adherence to a specified process.

@@

    Software quality is one of the most well studied aspects
    of software development.  Most of the work focuses on
    either the problems with the software or the source code.
    Quality and the number of problems with the software
    are inversely related, more problems means lower quality. 
    Quality is easy to measure, but 
    that measurement is usually very software specific.  It is easy
    to find that some software has $X$ number of problems, but
    it is nearly impossible to determine whether the quality
    of that software is better or worse than some other software
    with $X$ defects.  One piece of software can be 
    larger\footnote{Saying a piece of software is larger can be a 
    rather arbitrary statement.  It can mean the software requires 
    more computing time, has more lines of code, more documentation, 
    more hours spent on development, or some other arbitrary measure.}
    or more complex.  Thus, finding a value for quality is easier 
    than interpreting that value.  No matter the interpretation,
    the goal is to decrease the number of problems with the software.
    Top 10 lists have been created for techniques to remove problems
    from software \cite{Boehm2001}.  
    A number of different techniques or best practices
    for preventing defects have 
    been proposed \cite{Faizan2012}.  These are all strategies to identify
    or remove the problems before the software is completed and released
    to users.

@@

    One area of research that is focusing on the evaluation 
    of SDOs
    is \textit{software analytics}. 
    Software analytics is less focused on evaluation
    and more so on all sorts of analysis of software data.
    The earliest variants
    of software analytics were disguised as
    applications of data mining techniques to software 
    engineering data in the 
    late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
    Later the field began to emerge more heavily, but still
    remained primarily methods of data mining applied to 
    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
    The term software intelligence was proposed for the field of study
    \cite{Hassan2010}, but eventually
    the term software analytics became the dominant term for referring to the 
    field of study \cite{Buse2010, Zhang2011}.

@@

    All of these techniques are of no use if the correct data
    is not available.  Therefore, it is important to 
    identify the information that is needed to properly 
    perform software development analytics.
    Unfortunately, there are vast amounts of information that 
    need to be collected to meet the analytic needs of 
    developers and managers \cite{Buse2012}.  When the
    data and tools exist, the analytics should help an
    organization with the following tasks.
    \begin{itemize}
        \item Evaluate a project
        \item Determine what is and is not working
        \item Manage risk
        \item Anticipate changes
        \item Evaluate prior decisions
    \end{itemize}

### 2015-04-06 paper_20_sdo.tex
final updates before format check

\subsection{WHAT IS SOFTWARE ENGINEERING?}
\label{sec:swe}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  Institute of Electrical 
    and Electronics Engineers (IEEE) provides a definition that encompasses 
    many of the other definitions.
    \nomenclature{IEEE}{Institute of Electrical and Electronics Engineers}
    IEEE ISO610.12 defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

>>>>

\subsection{WHAT IS SOFTWARE ENGINEERING?}
\label{sec:swe}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  Institute of Electrical 
    and Electronics Engineers (IEEE) provides a definition that encompasses 
    many of the other definitions.
    \nomenclature{IEEE}{Institute of Electrical and Electronics Engineers}
    IEEE ISO610.12 defines software engineering as, 
    ``The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

### 2015-04-06 paper_40_cri.tex
final format check, added latest PDF
final updates before format check

    The scores for CRI will range from -1, indicating the worst 
    performance, all the way to +1, indicating perfection.
    A score of 0 is an indication of meeting the basic expectations. 
    A negative score indicates worse-than-expected performance and a 
    positive score indicates better-than-expected performance.   Here are some 
    examples. An CRI score of 0.35 means the organization is 
    performing 35\% better than expected.  Conversely, a score 
    of -0.15 means an organization is performing 15\% worse than expected.

    Below are the attributes of the CRI scoring.
    \begin{itemize}
        \item The range of scores must have equal values above and below 0
        \item The minimum score must equate to the worst possible 
            performance, however that is defined
        \item Similarly, the maximum score must equate to the best possible performance.  
        \item A score of 0 must be average (or expected) performance
        \item All individual elements must have the same scoring range
    \end{itemize}

@@

                1 & Software is unavailable and no workaround   \\
                \myrowcolour%
                2 & Software performance degraded with no workaround \\
                3 & Software performance degraded but workaround exists \\
                \myrowcolour%
                4 & Software functions but a loss of non-critical functionality \\
                5 & Others: minor cosmetic issue, missing documentation \\

@@

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects for Application ID $i$
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma_i^2$ is the estimated variance for Application $i$
                \end{itemize}

@@

                \begin{displaymath}
                   S_{2_i} = \left\{
                     \begin{array}{lr}
                       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}}\times k \right] \\
                       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}}\times k \right]
                     \end{array}
                   \right. \text{   , calculate availability score for each app $i$}
                \end{displaymath}

@@

                \begin{itemize}
                    \item $S_{2_i}$ is the availability score for System ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $A_{a_i}$ actual availability for System ID $i$
                    \item $A_{e_i}$ expected availability for System ID $i$
                \end{itemize}

@@

                \[
                    S_{3_i} = \sum^n_{i=1}\left( k \times \frac{ \sum^m_{j=1}a_{ij}-\frac{min + max}{2}}{m} \right)
                \]

                \begin{itemize}
                    \item $S_{3_i}$ is the satisfaction score for Question ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $a_{ij}$ answer to question $i$ for respondent $j$
                    \item $n$ number of questions
                    \item $m$ number of respondents
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

                Then the satisfaction score is calculated as below.  Use a weighted average
                to combine the question scores.

                \[
                    S_{3} = \sum\limits^n_{i=1} w_i S_{3_i}
                \]
                where
                \begin{itemize}
                    \item $S_3$ is the combined satisfaction score for all Questions IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                \end{itemize}

@@

                \begin{displaymath}
                    \Delta_i = \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the proportion the schedule was missed for project $i$
                \end{itemize}

@@

                \begin{equation}
                \label{eq:CDF}
                    S_{4_i} = 2k \cdot (CDF(\Delta_i) - \frac{1}{2})
                \end{equation}
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                \end{itemize}

@@

                \begin{displaymath}
                   S_{4_i} = \left\{
                     \begin{array}{lr}
                        \text{where } \Delta_i \geq 1 & : -1 \times k \\
                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times k  \\
                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times k
                     \end{array}
                   \right] \text{   , calculate schedule score for each project $i$}
                \end{displaymath}

                \[
                    S_{4} = \sum\limits^n_{i=1} w_i S_{4_i} 
                \]
                where
                \begin{itemize}
                    \item $S_4$ is the combined schedule score for all Project IDs, 
                    a weighted average
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                    \item $n$ is the number of projects
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the percent the schedule was missed
                    \item $\bar{\Delta}$ is the average percent schedules are missed
                    \item $S_{4_i}$ is the schedule score for project $i$
                \end{itemize}
                Then $S_4$ represents the CRI schedule score for that given time 
                frequency.
                Again, this was just an alternate approach to scoring schedule.  
                It will not be used in the case studies.

@@

                \begin{displaymath}
                   S_{5_i} = \left\{
                     \begin{array}{lr}
                       \text{where } R_{a_i} > b \times R_{s_i} & :  1 \times k \\
                       \text{where } R_{a_i} \leq R_{s_i} & : \left[ \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\times k \right] \\
                       \text{where } R_{a_i} > R_{s_i}  & : \left[ \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\times k \right]
                     \end{array}
                   \right. \text{   , calculate requirements score for each project $i$}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $S_{5_i}$ is the requirements score for Project ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $R_{a_i}$ actual requirements completed for Project ID $i$
                    \item $R_{s_i}$ expected requirements completed for Project ID $i$
                    \item $b$ multiplier to determine the upper bound
                \end{itemize}
                Then the requirements score is calculated as below.  
                Use a weighted average to combine the requirements scores
                from the Project IDs.

@@

            This weighted average allows for a score to be computed even when not
            all five elements are present. Just perform the weighted average with
            as many elements as present.  This technique allows CRI to implemented
            before data for all the elements has been collected.  Just begin
            to average elements as they become accessible.

>>>>

    The scores for CRI will range from -1, indicating the worst 
    performance, all the way to +1, indicating perfection.
    A score of 0 is an indication of meeting the basic expectations. 
    A negative score indicates worse-than-expected performance and a 
    positive score indicates better-than-expected performance.   For
    example, a CRI score of 0.35 means the organization is 
    performing 35\% better than expected.  Conversely, a score 
    of $-0.15$ means an organization is performing 15\% worse than expected.

    Below are the attributes of the CRI scoring.
    \begin{itemize}
        \item The range of scores must have equal values above and below 0.
        \item The minimum score must equate to the worst possible 
            performance, however that is defined.
        \item Similarly, the maximum score must equate to the best possible performance.  
        \item A score of 0 must be average (or expected) performance.
        \item All individual elements must have the same scoring range.
    \end{itemize}

@@

                1 & Software is unavailable with no workaround   \\
                \myrowcolour%
                2 & Software performance degraded with no workaround \\
                3 & Software performance degraded but workaround exists \\
                \myrowcolour%
                4 & Software functions but a loss of non-critical functionality \\
                5 & Others: minor cosmetic issue, missing documentation \\

@@

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \cdot k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \cdot k
                     \end{array} \right.
                   \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects for Application ID $i$
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma_i^2$ is the estimated variance for Application $i$
                \end{itemize}

@@

                \begin{displaymath}
                   S_{2_i} = \left\{
                     \begin{array}{lr}
                       \text{where } A_{a_i} \leq A_{e_i} & : \frac{A_{a_i} - A_{e_i}}{A_{e_i}}\cdot k  \\
                       \text{where } A_{a_i} > A_{e_i}  & : \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}}\cdot k
                     \end{array}
                   \right. \text{   , calculate availability score for each sys $i$}
                \end{displaymath}

@@

                \begin{itemize}
                    \item $S_{2_i}$ is the availability score for System ID $i$
                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                    \item $A_{a_i}$ is the actual availability for System ID $i$
                    \item $A_{e_i}$ is the expected availability for System ID $i$
                \end{itemize}

@@

                \[
                    S_{3_i} = k \cdot \frac{ \sum^m_{j=1}(\frac{2a_{ij}-min-max}{max-min})}{m}
                \]

                \begin{itemize}
                    \item $S_{3_i}$ is the satisfaction score for Question ID $i$
                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                    \item $a_{ij}$ is the answer to question $i$ for respondent $j$
                    \item $n$ is the number of questions
                    \item $m$ is the number of respondents
                    \item $min$ is the minimum score for a question
                    \item $max$ is the maximum score for a question
                \end{itemize}

                Then the satisfaction score is calculated as below.  Use a weighted average
                to combine the question scores:

                \[
                    S_{3} = \sum\limits^n_{i=1} w_i S_{3_i}
                \]
                where
                \begin{itemize}
                    \item $S_3$ is the combined satisfaction score for all Questions IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$.
                \end{itemize}

@@

                \begin{displaymath}
                    \Delta_i = \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $F_{a_i}$ is the actual finish date of project $i$
                    \item $F_{s_i}$ is the scheduled finish date of project $i$
                    \item $B_{s_i}$ is the scheduled beginning date of project $i$
                    \item $\Delta_i$ is the proportion the schedule was missed for project $i$
                \end{itemize}

@@

                \[
                \label{eq:CDF}
                    S_{4_i} = 2k \cdot \left(CDF(\Delta_i) - \frac{1}{2} \right)
                \]
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                \end{itemize}

@@

                \begin{displaymath}
                   S_{4_i} = \left\{
                     \begin{array}{lr}
                        \text{where } \Delta_i \geq 1 & : -1 \cdot k \\
                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \cdot k  \\
                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \cdot k
                     \end{array}
                   \right. \text{   , calculate schedule score for each project $i$}
                \end{displaymath}

                \[
                    S_{4} = \sum\limits^n_{i=1} w_i S_{4_i} 
                \]
                where
                \begin{itemize}
                    \item $S_4$ is the combined schedule score for all Project IDs, 
                    a weighted average
                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                    \item $n$ is the number of projects
                    \item $F_{a_i}$ is the actual finish date of project $i$
                    \item $F_{s_i}$ is the scheduled finish date of project $i$
                    \item $B_{s_i}$ is the scheduled beginning date of project $i$
                    \item $\Delta_i$ is the percent the schedule was missed
                    \item $\bar{\Delta}$ is the average percent schedules are missed
                    \item $S_{4_i}$ is the schedule score for project $i$
                \end{itemize}
                Then $S_4$ represents the CRI schedule score for that given time 
                frequency.
                Again, this was just an alternate approach to scoring schedule.  
                It will not be used in the case studies.

@@

                \begin{displaymath}
                   S_{5_i} = \left\{
                     \begin{array}{lr}
                       \text{where } R_{a_i} > b \cdot R_{s_i} & :  1 \cdot k \\
                       \text{where } R_{a_i} \leq R_{s_i} & : \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\cdot k \\
                       \text{where } R_{a_i} > R_{s_i}  & : \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\cdot k
                     \end{array}
                   \right. \text{   , calculate requirements score for each project $i$}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $S_{5_i}$ is the requirements score for Project ID $i$
                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                    \item $R_{a_i}$ is the actual requirements completed for Project ID $i$
                    \item $R_{s_i}$ is the expected requirements completed for Project ID $i$
                    \item $b$ is the multiplier to determine the upper bound
                \end{itemize}
                Then the requirements score is calculated as below.  
                Use a weighted average to combine the requirements scores
                from the Project IDs.

@@

            This weighted average allows for a score to be computed even when not
            all five elements are present. Just perform the weighted average with
            as many elements as present.  This technique allows CRI to be implemented
            before data for all the elements has been collected.  Just begin
            to average elements as they become accessible.
